Global adjoint tomography -- Model GLAD-M25

### 2018-10-15 main.tex
Updates from ShareLaTeX

\section{Starting Model GLAD--M15}

{\color{Red} Wenjie: Read for Jeroen to edit}

@@

...to be done...
We presented our model GLAD-M25, with S362ANI+M, S40RTS and EARA2014.
At 100km depth, our model shows sharpening at the Himalayas subductions
zones. At 250km, our models shows the subduction in the east part.
At 400km, our models shows the subduction at sumartra.

>>>>

\section{Starting Model GLAD-M15}

{\color{Red} Wenjie: Ready for Jeroen to edit}

@@

Asia has a very complicated tectonic settings, containing
the interaction among Indian, Euroasian, Australia, Pacific and Philippine
plates. Even though we don't have a significant large number of high
event-response stations at this region(compared to Europe and North
America), our inversion is compensated by the large number of temporary
arrays and earthquakes.

The southwestern part of china is featured by the Himalayas mountain, which is 
a shallow expression of the collision between India and Euroasian plate. Our
models shows a strong high-velocity anomalies near the plate boundary, and this
anomaly has all the way extending from 100km to 600km depth. With the increase
of depth, the high-velocity regions get sharper, indicating the narrowing
root of subduction plate. The high-elevation Tibetan plateau, sitting to
the north of Himalaya mountains, shows a relatively low velocity
comparing to its surroundings, including the Himalayas at its south and
Tianshan Mountain at is North, which is consistent with other global
and regional studies.

The southern part of Asia sees the majority tectonic activity between the Philippine
, EuroAsian and Australia plate. The Sumatra and Java trench, shown as sharp high-velocity
anomaly in our models below 200km, nicely follows the boundary between Euroasian
and Australia plates. This feature stays still very sharp at the 600km and extend
down to 1000km. We will have more detailed discussion about it in the following sections.
The Malina and Philippine Trench is also much sharper in our model between 200km and
600km.
The eastern part has a series of trenches, including Japan Trench, Izu-Bonin Trench,
Mariana Trench from North to the South. All those features follows perfectly with
the plate boundary, as emerging features compared the two global models from 200km
to 400km depth. At 100km depth, our model is strengthening the low-velocity structures
in the east of Philippine Plate and the anomaly gradually moved to the west at 200km
depth. In the north, our models shows low-velocity structures associated
with the Altay-Sayan and Baikai rift systems.

Other than the boundaries, our models also show much more details at the
intra-plate tectonic activities. It has good correlation of low-velocity regions with
the Hainan spot and Changbai Volcanoes. Those low-velocity features is prominent at
shallow depth, but gradually reduce its magnitude down with the increase of
depth, indicating that those features might be lithosphere's activity rather
than deep mantle's.
The Sichuan basin, a very localized high-velocity structures, is extending below
250km depth. At 600km, most of the models shows a large regions of high-velocities
near the Philippine plate, indicating the pounding of ancient subducted plates.
